Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
empty rust table for Kush

% ---------------- C++ table UM Only--------------------------
\begin{table}[hbtp]
\centering
\caption{Regex vs. Comby for C++ (top) and Java (bottom)}
\label{tab:table_cpp1java}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule
\mc{6}{c}{\textbf{C++}} \\\midrule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
ompl & 525 & $\frac{595}{2533}$ & 23.49\% &  $\frac{564}{2127}$  & 25.94\%   \\[1ex]
libgraphqlparser& 137 & $\frac{157}{741}$ & 21.19\%  & $\frac{131}{440}$ & 29.77\% \\[1ex]
rethinkdb\_rebirth &471 &  $\frac{545}{2246}$ & 24.27\% & $\frac{492}{2009}$ & 24.49\% \\[1ex]
xoreos & 732  & $\frac{2419}{3876}$  & 62.41\% & $\frac{2280}{3297}$ & 69.15\% \\[1ex]
libxmljs &630 &  $\frac{881}{3989}$ & 22.09\% & $\frac{790}{4008}$ & 19.71\% \\[1ex]
tiny-diff.-simulator &  195 & $\frac{747}{1282}$ &58.27\% &$\frac{770}{1214}$ & 63.43\% \\[1ex]
\bottomrule
\end{tabularx}
 \begin{tabularx}{\columnwidth}{Xllrrr}
                  & &       & Valid  & Invalid  & \% \\\midrule
 \multirow{6}{*}{\textbf{Overall}} & \multirow{3}{*}{Regex} & Mean     & 890.67 &  1553.83 & 35.28\% \\
                          & & Med.    & 671.00 & 1579.00  & 23.88\%   \\
                          & & Std.Dev. & 787.62 & 956.31   & 19.48\%  \\\cline{2-6}
  & \multirow{3}{*}{Comby}  & Mean     & 837.83 & 1352.50 & 38.75\%  \\
                         & & Med.    & 667.00 & 1267.00 & 27.86\%  \\
                         & & Std.Dev. & 745.78 & 1058.33& 21.66\%  \\\bottomrule
 \end{tabularx}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule
\mc{6}{c}{\textbf{Java}} \\\midrule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
 pebble         & 279 & $\frac{86}{1014}$ & 8.48\% & $\frac{85}{752}$ & 11.30\%  \\[1ex]
 spring-hateoas & 397 & $\frac{248}{2479}$ & 10.00\% & $\frac{172}{1384}$ & 12.43\%  \\[1ex]
 javacc         & 363 & $\frac{542}{1888}$ & 28.70\% & $\frac{494}{1281}$ & 38.71\%  \\[1ex]
 coffee-gb      & 463 & $\frac{224}{1927}$ & 11.63\% & $\frac{174}{798}$ & 21.80\% \\[1ex]
 egads          & 252 & $\frac{624}{2427}$ & 25.43\% & $\frac{597}{1163}$ & 51.33\%  \\[1ex]
 apk-parser     & 324 & $\frac{351}{1583}$ & 22.17\% & $\frac{333}{1199}$ & 27.77\%  \\[1ex]\midrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrr}
              & & & Valid  & Invalid  & \% \\\midrule
\multirow{6}{*}{\textbf{Overall}} & \mr{3}{Regex} & Mean     &  345.83 & 1545.00  & 17.74\% \\
              &   & Med.     & 299.50 & 1524.50 & 16.90\%  \\
              &   & Std.Dev. & 203.86 & 467.98 & 8.73\%  \\\cline{2-6}
& \mr{3}{Comby} & Mean     & 309.17 & 786.17 & 27.22\% \\
              &   & Med.     & 253.50 & 724.50 & 24.79\% \\
              &   & Std.Dev. & 202.44 & 235.24  & 15.59\% \\\bottomrule
\end{tabularx}
\end{table}

@@

% ---------------- Python table UM Only --------------------------

@@

>>>>

% ---------------- C++ table UM Only--------------------------
\begin{table}[hbtp]
\centering
\caption{Regex vs. Comby for C++ (top) and Java (bottom)}
\label{tab:table_cpp1java}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule\toprule
\mc{6}{c}{\textbf{C++}} \\\midrule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
ompl & 525 & $\frac{595}{2533}$ & 23.49\% &  $\frac{564}{2127}$  & 25.94\%   \\[1ex]
libgraphqlparser& 137 & $\frac{157}{741}$ & 21.19\%  & $\frac{131}{440}$ & 29.77\% \\[1ex]
rethinkdb\_rebirth &471 &  $\frac{545}{2246}$ & 24.27\% & $\frac{492}{2009}$ & 24.49\% \\[1ex]
xoreos & 732  & $\frac{2419}{3876}$  & 62.41\% & $\frac{2280}{3297}$ & 69.15\% \\[1ex]
libxmljs &630 &  $\frac{881}{3989}$ & 22.09\% & $\frac{790}{4008}$ & 19.71\% \\[1ex]
tiny-diff.-simulator &  195 & $\frac{747}{1282}$ &58.27\% &$\frac{770}{1214}$ & 63.43\% \\[1ex]
\bottomrule
\end{tabularx}
 \begin{tabularx}{\columnwidth}{Xllrrr}
                  & &       & Valid  & Invalid  & \% \\\midrule
 \multirow{6}{*}{\textbf{Overall}} & \multirow{3}{*}{Regex} & Mean     & 890.67 &  1553.83 & 35.28\% \\
%                          & & Med.    & 671.00 & 1579.00  & 23.88\%   \\
                          & & Std.Dev. & 787.62 & 956.31   & 19.48\%  \\\cline{2-6}
  & \multirow{3}{*}{Comby}  & Mean     & 837.83 & 1352.50 & 38.75\%  \\
%                         & & Med.    & 667.00 & 1267.00 & 27.86\%  \\
                         & & Std.Dev. & 745.78 & 1058.33& 21.66\%  \\\bottomrule
 \end{tabularx}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule
\mc{6}{c}{\textbf{Java}} \\\midrule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
 pebble         & 279 & $\frac{86}{1014}$ & 8.48\% & $\frac{85}{752}$ & 11.30\%  \\[1ex]
 spring-hateoas & 397 & $\frac{248}{2479}$ & 10.00\% & $\frac{172}{1384}$ & 12.43\%  \\[1ex]
 javacc         & 363 & $\frac{542}{1888}$ & 28.70\% & $\frac{494}{1281}$ & 38.71\%  \\[1ex]
 coffee-gb      & 463 & $\frac{224}{1927}$ & 11.63\% & $\frac{174}{798}$ & 21.80\% \\[1ex]
 egads          & 252 & $\frac{624}{2427}$ & 25.43\% & $\frac{597}{1163}$ & 51.33\%  \\[1ex]
 apk-parser     & 324 & $\frac{351}{1583}$ & 22.17\% & $\frac{333}{1199}$ & 27.77\%  \\[1ex]\midrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrr}
              & & & Valid  & Invalid  & \% \\\midrule
\multirow{6}{*}{\textbf{Overall}} & \mr{3}{Regex} & Mean     &  345.83 & 1545.00  & 17.74\% \\
%              &   & Med.     & 299.50 & 1524.50 & 16.90\%  \\
              &   & Std.Dev. & 203.86 & 467.98 & 8.73\%  \\\cline{2-6}
& \mr{3}{Comby} & Mean     & 309.17 & 786.17 & 27.22\% \\
%              &   & Med.     & 253.50 & 724.50 & 24.79\% \\
              &   & Std.Dev. & 202.44 & 235.24  & 15.59\% \\\bottomrule
\end{tabularx}
\end{table}

@@

\iffalse
\begin{table}[hbtp]
\centering
\caption{Regex vs. Comby for Python++, including redundant mutants.}
\label{tab:table_pyrust}
\begin{tabularx}{\columnwidth}{X|r|rcr|rcr}
\toprule\toprule
\mc{6}{c}{\textbf{Python++}} \\\midrule
                 &                 & \multicolumn{3}{c|}{\textbf{Regex}}             &\multicolumn{3}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC}    & redundant & $\frac{valid}{total}$ & \textbf{\%} & redundant & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
keract           & 402             & 729       & $\frac{1655}{3984}$   & 41.53\%     & 533       & $\frac{1471}{3067}$   & 47.96\% \\[1ex]
dtw              & 118             & 567       & $\frac{973}{2106}$    & 46.20\%     & 639       & $\frac{866}{1836}$    & 47.19\% & \\[1ex]
notion-sdk-py    & 189             & 82        & $\frac{196}{1038}$    & 18.89\%     & 122       & $\frac{196}{1019}$    & 19.23\% & \\[1ex]
{\makecell{atlassian-python \\ api}} & 236 & $\frac{302}{1304}$  & 207  &	19.99\% & \multirow{2}{*}{236}\\\cline{2-7}
       & \multicolumn{2}{c|}{Comby} & 333  & 635  & 351  & 25.25\% & \\ \hline
ESD    & 698 & $\frac{1859}{4626}$  & 1642  & 29.46\% & \multirow{2}{*}{698}\\\cline{2-7}
       & \multicolumn{2}{c|}{Comby} & 1712  & 1548  &	614  & 44.18\% & \\ \hline
fiber  & 358 & $\frac{493}{1402}$  & 163  & 31.08\% & \multirow{2}{*}{358}\\\cline{2-7}
       & \multicolumn{2}{c|}{Comby} & 458  & 767 	& 241  & 31.24\% & \\ \hline

\multirow{6}{*}{Overall} & \multirow{3}{*}{Regex} & Mean & 913.00 & 1267.33 & 565.00 & 31.19\%  & \\\cline{3-7}
    &   &  Std. Dev & 708.93 & 813.35 & 584.79 & 11.06\%  & \\\cline{2-7}

 & \multirow{3}{*}{Comby} & Mean & 839.33 & 840.67 & 416.67 & 35.84\% & \\\cline{3-7}
    &   &  Std. Dev & 628.79 & 418.99 & 211.62 & 12.28\%  & \\\hline
\end{tabularx}
\end{table}
\fi
% ---------------- Python table UM Only --------------------------

@@

% ---------------- Rust table UM Only --------------------------
\begin{table}[hbtp]
\centering
{\small
\caption{Rust (Regex vs. Comby)}
\label{tab:table_rust1}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
cargo release    & ...    & & & \\[1ex]
\end{tabularx}
 \begin{tabularx}{\columnwidth}{Xllrrr}
               & & & Valid  & Invalid  & \% \\\midrule
 \multirow{6}{*}{\textbf{Overall}} & \mr{3}{Regex} & Mean     &   &  & \\
               &   & Std.Dev. & &  &   \\\cline{2-6}
 & \mr{3}{Comby} & Mean     &  &  &  \\
 %              &   & Med.     & 253.50 & 724.50 & 24.79\% \\
               &   & Std.Dev. & &  &   \\\bottomrule
\end{tabularx}}
\end{table}

\begin{table}[hbtp]
\centering
\caption{Rust (Regex vs. Comby)}
\label{tab:table_rust1}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{|c|c|c|r|r|r|c|}
\hline
 & \multicolumn{2}{c|}{} & \textbf{Valid} & \textbf{Invalid} & \textbf{Valid \%} &  \textbf{LOC} \\ \hline
\multirow{2}{*}{cargo release} & \multicolumn{2}{c|}{Regex} & 851 \hspace{8pt} &	1163 \hspace{8pt} & 42.25\%  & \multirow{2}{*}{346}\\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 1690 \hspace{8pt} & 711 \hspace{8pt} & 70.39\% & \\ \hline
\multirow{2}{*}{passerine} & \multicolumn{2}{c|}{Regex} & 213 \hspace{8pt} & 2081 \hspace{8pt} & 9.29\% & \multirow{2}{*}{376}\\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 173 \hspace{8pt} & 1518 \hspace{8pt} & 10.23\% & \\ \hline
\multirow{2}{*}{typos} & \multicolumn{2}{c|}{Regex} & 386 \hspace{8pt} & 1534 \hspace{8pt} & 20.10\% & \multirow{2}{*}{463}\\\cline{2-6}
    & \multicolumn{2}{c|}{Comby} & 366 \hspace{8pt} & 1199 \hspace{8pt} &	 23.39\% & \\ \hline

 & \multirow{3}{*}{Comby} & Mean & 554.00 & 1055.83	& 29.29\% & \\\cline{3-6}
    &   &  Median & 384.00 & 1059.50	& 25.60\%  & \\\cline{3-6}
    &   &  Std. Dev & 592.63 & 508.30 & 21.63\%  & \\\hline
\end{tabular}
